PM Mungbean meta-analysis

### 2021-03-09 02_Preliminary_analysis.Rmd
update code from crop_rain()

unique(PM_MB_dat[,c("location","lat","lon")])
PM_MB_dat[is.na(PM_MB_dat$lat),]

trials <- unique(PM_MB_dat, c("location","lat","lon"))
apply(trials,1, function(LL) {

   stat_sweep <- bomrang::sweep_for_stations(as.numeric(c(LL["lat"],LL["lon"])))

   # Remove banned stations
   banned_stations <- c("055286") # stations don't report rain
   stat_sweep <- stat_sweep[stat_sweep$site != banned_stations,]

   statID <- paste(stat_sweep[1,"name"],stat_sweep[1,"site"], sep = "_")

   return(statID)

})
bomrang::sweep_for_stations(unlist(PM_MB_dat[1,c("lat","lon")]))

bomrang::get

# Obtain rainfall from bomrang
PM_MB_dat$sum_rain <-
   apply(PM_MB_dat, 1, function(x) {
      crop_rain(
         latitude = x["lat"],
         longitude = x["lon"],
         start = x["planting_date"],
         end = x["harvest_date"]
      )
   })

@@

```{r early_season_rain}
PM_MB_dat$early_rain <-
   apply(PM_MB_dat, 1, function(x) {
      crop_rain(
         latitude = x["lat"],
         longitude = x["lon"],
         start = x["planting_date"],
         end = x["first_sign_disease"]
      )
   })

@@

```{r late_rain}
PM_MB_dat$late_rain <-
   apply(PM_MB_dat, 1, function(x) {
      crop_rain(
         latitude = x["lat"],
         longitude = x["lon"],
         start = x["first_sign_disease"],
         end = x["harvest_date"]
      )
   })

@@

#### Mid-season rainfall  
Here we only look at the effect of rainfall between the 20 days after planting and 80 days after planting.
```{r mid_rain}
PM_MB_dat$mid_rain <-
   apply(PM_MB_dat, 1, function(x) {
      crop_rain(
         latitude = x["lat"],
         longitude = x["lon"],
         start = ymd(x["planting_date"]) + days(20),
         end = ymd(x["planting_date"]) + days(80)
      )
   })

>>>>

# Obtain rainfall from bomrang

crop_rain(location_name = PM_MB_dat$location,
          latitude = PM_MB_dat$lat,
          longitude = PM_MB_dat$lon,
          first_day = PM_MB_dat$planting_date,
          last_day = PM_MB_dat$harvest_date)

PM_MB_dat$sum_rain <-
   crop_rain(location_name = PM_MB_dat$location,
          latitude = PM_MB_dat$lat,
          longitude = PM_MB_dat$lon,
          first_day = PM_MB_dat$planting_date,
          last_day = PM_MB_dat$harvest_date)

@@

```{r early_season_rain}
PM_MB_dat$early_rain <-
   crop_rain(location_name = PM_MB_dat$location,
          latitude = PM_MB_dat$lat,
          longitude = PM_MB_dat$lon,
          first_day = PM_MB_dat$planting_date,
          last_day = PM_MB_dat$first_sign_disease)

@@

```{r late_rain}
PM_MB_dat$late_rain <-
   crop_rain(location_name = PM_MB_dat$location,
          latitude = PM_MB_dat$lat,
          longitude = PM_MB_dat$lon,
          first_day = PM_MB_dat$first_sign_disease,
          last_day = PM_MB_dat$harvest_date)

@@

#### Mid-season rainfall  
Here we only look at the effect of rainfall between the 20 days after planting and 80 days after planting.
```{r mid_rain}
PM_MB_dat$mid_rain <-
   crop_rain(location_name = PM_MB_dat$location,
          latitude = PM_MB_dat$lat,
          longitude = PM_MB_dat$lon,
          first_day = ymd(PM_MB_dat$planting_date) + days(20),
          last_day = ymd(PM_MB_dat$planting_date) + days(80)
   )
